### 2014-10-12 Neutral_simulPow.Rmd
add parallel simulNeutral_1Time function

require(ggplot2)
pow_GC1$MeanSp <- as.numeric(pow_GC1$MeanSp)
pow_GC1$power <- as.numeric(pow_GC1$power)
pow_GC1$typeI <- as.numeric(pow_GC1$typeI)

@@

```{r more_simul512_LogSerParms, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

simul <- rbind(simul,simulNeutral_1Time(8,512,500,"L",20,F))
simul <- rbind(simul,simulNeutral_1Time(64,512,500,"L",20,F))
simul <- rbind(simul,simulNeutral_1Time(256,512,500,"L",20,F))

```{r more_simul256_LogSerParms, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

simul <- rbind(simul,simulNeutral_1Time(8,256,500,"L",20,F))
simul <- rbind(simul,simulNeutral_1Time(64,256,500,"L",20,F))
simul <- rbind(simul,simulNeutral_1Time(256,256,500,"L",20,F))

setwd(oldcd)
save.image()
```
Using the GC with q<=10

```{r power_GCq10test, eval=T,echo=F,message=T,warning=T}
setwd("Simul")
# sim1 <- data.frame(nsp=65,side=256,time=100,meta="L",spMeta=87,rep=3)
#
#cc <- powerNeutral_1T_GC(simul[1,],3,0.2,0.04,0.001,10)

@@

cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1T_GC(simul[i,],3,0.2,0.04,0.001,10)
}
pow_GCq10 <- data.frame()
comp_GCq10<- data.frame()

@@

>>>>

require(ggplot2)
pow_GC1$MeanSp <- as.numeric(pow_GC1$MeanSp)
pow_GC1$power <- as.numeric(pow_GC1$power)
pow_GC1$typeI <- as.numeric(pow_GC1$typeI)

@@

```{r more_simul512_LogSerParms, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

ps <- data.frame(nsp=c(8,64,256),si=rep(c(512,256),each=3))
require(doParallel)
cn <-detectCores()
cl <- makeCluster(cn)
registerDoParallel(cl)

simul <- foreach(i=1:nrow(ps),.combine='rbind') %dopar%
{
    print(ps[i,])
    simulNeutral_1Time(ps$nsp[i],ps$si[i],500,"L",20,F)
}
stopCluster(cl)

setwd(oldcd)
rm(ps,cn,cl)
save.image()
```

Compare using the GC with q<=10

```{r power_GCq10test, eval=F,echo=F,message=T,warning=T}
setwd("Simul")

@@

cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1T_GC(simul[i,],3,0,0,0.001,10)
}
pow_GCq10 <- data.frame()
comp_GCq10<- data.frame()

@@

setwd(oldcd)
rm(cc)
save.image()

The power of compareGrowthCurves is much much greater using the range -10 10 than -24 24, and type I error is lower!!

Lets try with ANderson-Darling test!

```{r power_ADq10test, eval=F,echo=F,message=T,warning=T}
setwd("Simul")

cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1Time(simul[i,],0.2,0.04,0.001,10)
}
pow_ADq10 <- data.frame()
comp_ADq10<- data.frame()

  pow_ADq10 <- rbind(pow_ADq10, cc[[i]]$pow_AD)
  comp_ADq10<- rbind(comp_ADq10,cc[[i]]$comp_AD)
  }

setwd(oldcd)
rm(cc)
save.image()
